Hierarchically Supervised Latent Dirichlet Allocation

### 2011-05-30 paper/main.tex
Updated figure and minor changes to evaluation

\subsection{Evaluation}
%\begin{itemize}
%\item Talk about hierarchy and no hierarchy
%\item Make explicit calculation of sensitivity and 1-specificity
%\end{itemize}
For each dataset, a held out set of 1,000 documents and accompanying
labels were used for evaluation. The two main methods of evaluation
for the model are prediction and topic quality. To evaluate predictive
performance for all comparison models equivalently, each model was
evaluated with two methods. The first method augmented the observed
labels in the held out set as well as their ancestors in the hierarchy
as

\subsubsection{Prediction}

The two measures for predictive performance used here include the
true positive rate and the false positive rate. We evaluate model
performance on held out data. A more ideal evaluation of performance
would include a manually labeled hierarchy since it is well known
that ICD-9 codes have a relatively low sensitivity.

Performance was evaluated against $p\left(y_{l,\hat{d}}\mid w_{1:N,d}\right)$.

\subsubsection{Topic Quality and Character}

TBD

>>>>

\subsection{Evaluation}

%\begin{itemize}
%\item Talk about hierarchy and no hierarchy
%\item Make explicit calculation of sensitivity and 1-specificity
%\end{itemize}
For each dataset, a held out set of 1,000 documents and accompanying
labels were used for evaluation. The two main methods of evaluation
for the model are prediction and topic quality. To evaluate predictive
performance for all comparison models equivalently, each model was
evaluated with two methods. The first evaluation method augments the
observed labels in the held out set with their ancestors and considers
all other non-existant labels to be negative. The second method ignores
the ancestors of the observed labels in the held out set and considers
all other non-existant labels to be negative. This uniform treatment
of ancestors allows for a fair comparison of the models.

The two measures for predictive performance used here include the
true positive rate and the false positive rate evaluated based on
$p\left(y_{l,\hat{d}}\mid w_{1:N,d}\right)$ for each label in each
model.
